Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-14 GWLDCII.tex
changes from on the phone

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below. For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$. \sanote{not putting sections here, but I'd like a second thought -- what is this in response to?} \sanote{I'm not sure  at this point. }

@@

This would certainly hold if  the singularities in the integrands $\Omega(W)$ (the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel. Specifically, it is conjectured that these poles cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples (e.g. \cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.\hlfix{}{Is this updated for the spurious vs physical poles?}  \sanote{these arre all spurioous poles. Needs  more?}

@@

A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations. \sanote{I don't think I need to say more for point 2 of report Y? -- maybe we should say ``differential form'' somewhere.  Let's discuss.}

>>>>

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.

The differential form $\Omega(W)$ is playing a similar role to that of volume forms in the Amplituhedron literature.
For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.

@@

This would certainly hold if the singularities in the integrands $\Omega(W)$ cancel out in the sum.  The singularities coming from the zeros of $R(W)$ are the spurious poles of the theory and the physical theory tells us that they should cancel. 
%(the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel.
Specifically, it is conjectured that these poles cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples (e.g. \cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.

@@

In order to compute the contribution of this diagram to the tree level scattering amplitude one needs only to localize the differential form $\Omega(W)$ with respect to a delta function that evaluates the matrix $C(W)$ at the external momenta.

A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
